Technique for \earlywarning\ detection of compact binary coalescence and its implication for multimessenger astronomy

### 2011-06-01 results.tex
added figure
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@806 ccdd05d5-56c1-461a-bf98-85f6876523b4
some section headings
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@809 ccdd05d5-56c1-461a-bf98-85f6876523b4

>>>>

In this section we test our implementation of the \lloid\ method using the
pipeline described in the previous section.  We answer the following questions
\begin{itemize}
\item What is the measured loss of SNR due to the approximations used in the \lloid\ algorithm in a realistic analysis pipeline?
\item What is the measured latency of the implementation described in section 
\ref{sec:implementation}?
\item What is the measured computational cost of the implementation described in section
\ref{sec:implementation}?
\end{itemize}

\subsection{Measured \SNR\ loss}

\begin{figure}
\includegraphics{resamp_mm.pdf}
\caption{\label{fig:resamp_mm}}
\end{figure}

\subsection{Measured latency}

\subsection{Measured computational cost}
